---
title: "Exploratory Volatility Calculations"
author: "Holly Bossart"
date: "February 20, 2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(TTR)
library(tidyverse)

source("R/volatilityfunctions.R")

data = read.csv("Data/OHLCprices2.csv")
ticker = data.frame(unique(data$TICKER))
names(ticker)[1] <- "Company"


```

## 30 Companies
Data collected from WRDS CRSP Database.

```{r}
data$COMNAM[data$COMNAM == 'WAL MART STORES INC'] <- 'WALMART INC'
comnames <- data.frame(unique(data$COMNAM))
comnames

```



```{r, echo=FALSE}
oracle <- filter(data, data$COMNAM == 'ORACLE CORP')
microsoft <- filter(data, data$COMNAM == 'MICROSOFT CORP')
exxon <- filter(data, data$COMNAM == 'EXXON MOBIL CORP')
gm <- filter(data, data$COMNAM == 'GENERAL MOTORS CO')
ibm <- filter(data, data$COMNAM == 'INTERNATIONAL BUSINESS MACHS COR')
facebook <- filter(data, data$COMNAM == 'FACEBOOK INC')
chevron <- filter(data, data$COMNAM == 'CHEVRON CORP NEW')
apple <- filter(data, data$COMNAM == 'APPLE INC')
alibaba <- filter(data, data$COMNAM == 'ALIBABA GROUP HOLDING LTD')
pg <- filter(data, data$COMNAM == 'PROCTER & GAMBLE CO')
pfizer <- filter(data, data$COMNAM == 'PFIZER INC')
johnson <- filter(data, data$COMNAM == 'JOHNSON & JOHNSON')
disney <- filter(data, data$COMNAM == 'DISNEY WALT CO')
wellsfargo <- filter(data, data$COMNAM == 'WELLS FARGO & CO NEW')
jpmorgan <- filter(data, data$COMNAM == 'JPMORGAN CHASE & CO')
walmart <- filter(data, data$COMNAM == 'WALMART INC')
intel <- filter(data, data$COMNAM == 'INTEL CORP')
bankofa <- filter(data, data$COMNAM == 'BANK OF AMERICA CORP')
verizon <- filter(data, data$COMNAM == 'VERIZON COMMUNICATIONS INC')
att <- filter(data, data$COMNAM == 'A T & T INC')
homedep <- filter(data, data$COMNAM == 'HOME DEPOT INC')
citi <- filter(data, data$COMNAM == 'CITIGROUP INC')
amazon <- filter(data, data$COMNAM == 'AMAZON COM INC')
chinamob <- filter(data, data$COMNAM == 'CHINA MOBILE LTD')
taiwan <- filter(data, data$COMNAM == 'TAIWAN SEMICONDUCTOR MFG CO LTD')
novartis <- filter(data, data$COMNAM == 'NOVARTIS A G')
visa <- filter(data, data$COMNAM == 'VISA INC')
unhealth <- filter(data, data$COMNAM == 'UNITEDHEALTH GROUP INC')
busch <- filter(data, data$COMNAM == 'ANHEUSER BUSCH INBEV SA NV')
netflix <- filter(data, data$COMNAM == 'NETFLIX INC')


```

## Plotting Closing Price or Bid/Ask Average and Volatility

### Oracle

#### Summary of Price Data
```{r, echo=FALSE}
# making the data into time series plots
oracle.p.t <- ts(oracle$PRC, start = c(2015,1,1), frequency = 251.6)
summary(oracle.p.t)

```


```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(oracle.p.t, ylim=c(30,75),xlab="2015-2019",main="Oracle Closing Prices 01/01/2015-12/31/2019")


```

#### Summary of Volatility Data
```{r, echo=FALSE}
summary(garmanklassTA(oracle$OPENPRC, oracle$ASKHI, oracle$BIDLO, oracle$PRC))
par(mfrow=c(1,1), mex=0.75)
plot.ts(garmanklassTA(oracle$OPENPRC, oracle$ASKHI, oracle$BIDLO, oracle$PRC), ylab="GK volatility", main = "Oracle Volatility 01/02/2015-12/31/2019")

```

```{r, echo=FALSE}
oracle.v <- garmanklassTA(oracle$OPENPRC, oracle$ASKHI, oracle$BIDLO, oracle$PRC)
oracle.v <- oracle.v[-1]
oracle.v <- ts(oracle.v, start = c(2015,1,2), frequency = 251.4)

```



### Microsoft

#### Summary of Price Data
```{r, echo=FALSE}
microsoft.p.t <- ts(microsoft$PRC, start = c(2015,1,1), frequency = 251.6)
summary(microsoft.p.t)

```

```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(microsoft.p.t, ylim=c(30,175),xlab="2015-2019",main="microsoft Closing Prices 01/01/2015-12/31/2019")

```

#### Summary of Volatility Data
```{r, echo=FALSE}
summary(garmanklassTA(microsoft$OPENPRC, microsoft$ASKHI, microsoft$BIDLO, microsoft$PRC))
par(mfrow=c(1,1), mex=0.75)
plot.ts(garmanklassTA(microsoft$OPENPRC, microsoft$ASKHI, microsoft$BIDLO, microsoft$PRC), ylab="GK volatility", main = "microsoft Volatility 01/02/2015-12/31/2019")

```

```{r, echo=FALSE}
microsoft.v <- garmanklassTA(microsoft$OPENPRC, microsoft$ASKHI, microsoft$BIDLO, microsoft$PRC)
microsoft.v <- microsoft.v[-1]
microsoft.v <- ts(microsoft.v, start = c(2015,1,2), frequency = 251.4)

```


### Exxon
#### Summary of Price Data
```{r, echo=FALSE}
exxon.p.t <- ts(exxon$PRC, start = c(2015,1,1), frequency = 251.6)
summary(exxon.p.t)

```

```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(exxon.p.t, ylim=c(60,100),xlab="2015-2019",main="exxon Closing Prices 01/01/2015-12/31/2019")

```


#### Summary of Volatility Data
```{r, echo=FALSE}
summary(garmanklassTA(exxon$OPENPRC, exxon$ASKHI, exxon$BIDLO, exxon$PRC))
par(mfrow=c(1,1), mex=0.75)
plot.ts(garmanklassTA(exxon$OPENPRC, exxon$ASKHI, exxon$BIDLO, exxon$PRC), ylab="GK volatility", main = "exxon Volatility 01/02/2015-12/31/2019")

```

```{r, echo=FALSE}
exxon.v <- garmanklassTA(exxon$OPENPRC, exxon$ASKHI, exxon$BIDLO, exxon$PRC)
exxon.v <- exxon.v[-1]
exxon.v <- ts(exxon.v, start = c(2015,1,2), frequency = 251.4)

```



### General Motors
#### Summary of Price Data
```{r, echo=FALSE}
gm.p.t <- ts(gm$PRC, start = c(2015,1,1), frequency = 251.6)
summary(gm.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(gm.p.t, ylim=c(20,55),xlab="2015-2019",main="gm Closing Prices 01/01/2015-12/31/2019")

```

#### Summary of Volatility Data
```{r, echo=FALSE}
summary(garmanklassTA(gm$OPENPRC, gm$ASKHI, gm$BIDLO, gm$PRC))
par(mfrow=c(1,1), mex=0.75)
plot.ts(garmanklassTA(gm$OPENPRC, gm$ASKHI, gm$BIDLO, gm$PRC), ylab="GK volatility", main = "gm Volatility 01/02/2015-12/31/2019")

```

```{r, echo=FALSE}
gm.v <- garmanklassTA(gm$OPENPRC, gm$ASKHI, gm$BIDLO, gm$PRC)
gm.v <- gm.v[-1]
gm.v <- ts(gm.v, start = c(2015,1,2), frequency = 251.4)

```


### IBM
#### Summary of Price Data
```{r, echo=FALSE}
ibm.p.t <- ts(ibm$PRC, start = c(2015,1,1), frequency = 251.6)
summary(ibm.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(ibm.p.t, ylim=c(100,190),xlab="2015-2019",main="ibm Closing Prices 01/01/2015-12/31/2019")

```

#### Summary of Volatility Data
```{r, echo=FALSE}
summary(garmanklassTA(ibm$OPENPRC, ibm$ASKHI, ibm$BIDLO, ibm$PRC))
par(mfrow=c(1,1), mex=0.75)
plot.ts(garmanklassTA(ibm$OPENPRC, ibm$ASKHI, ibm$BIDLO, ibm$PRC), ylab="GK volatility", main = "ibm Volatility 01/02/2015-12/31/2019")

```

```{r, echo=FALSE}
ibm.v <- garmanklassTA(ibm$OPENPRC, ibm$ASKHI, ibm$BIDLO, ibm$PRC)
ibm.v <- ibm.v[-1]
ibm.v <- ts(ibm.v, start = c(2015,1,2), frequency = 251.4)

```


### Facebook
#### Summary of Price Data
```{r, echo=FALSE}
facebook.p.t <- ts(facebook$PRC, start = c(2015,1,1), frequency = 251.6)
summary(facebook.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(facebook.p.t, ylim=c(70,230),xlab="2015-2019",main="facebook Closing Prices 01/01/2015-12/31/2019")

```

#### Summary of Volatility Data
```{r, echo=FALSE}
summary(garmanklassTA(facebook$OPENPRC, facebook$ASKHI, facebook$BIDLO, facebook$PRC))
par(mfrow=c(1,1), mex=0.75)
plot.ts(garmanklassTA(facebook$OPENPRC, facebook$ASKHI, facebook$BIDLO, facebook$PRC), ylab="GK volatility", main = "facebook Volatility 01/02/2015-12/31/2019")

```

```{r, echo=FALSE}
facebook.v <- garmanklassTA(facebook$OPENPRC, facebook$ASKHI, facebook$BIDLO, facebook$PRC)
facebook.v <- facebook.v[-1]
facebook.v <- ts(facebook.v, start = c(2015,1,2), frequency = 251.4)

```



### Chevron
#### Summary of Price Data
```{r, echo=FALSE}
chevron.p.t <- ts(chevron$PRC, start = c(2015,1,1), frequency = 251.6)
summary(chevron.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(chevron.p.t, ylim=c(60,145),xlab="2015-2019",main="chevron Closing Prices 01/01/2015-12/31/2019")

```

#### Summary of Volatility Data
```{r, echo=FALSE}
summary(garmanklassTA(chevron$OPENPRC, chevron$ASKHI, chevron$BIDLO, chevron$PRC))
par(mfrow=c(1,1), mex=0.75)
plot.ts(garmanklassTA(chevron$OPENPRC, chevron$ASKHI, chevron$BIDLO, chevron$PRC), ylab="GK volatility", main = "chevron Volatility 01/02/2015-12/31/2019")

```

```{r, echo=FALSE}
chevron.v <- garmanklassTA(chevron$OPENPRC, chevron$ASKHI, chevron$BIDLO, chevron$PRC)
chevron.v <- chevron.v[-1]
chevron.v <- ts(chevron.v, start = c(2015,1,2), frequency = 251.4)

```



### Apple
#### Summary of Price Data
```{r, echo=FALSE}
apple.p.t <- ts(apple$PRC, start = c(2015,1,1), frequency = 251.6)
summary(apple.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(apple.p.t, ylim=c(80,300),xlab="2015-2019",main="apple Closing Prices 01/01/2015-12/31/2019")

```


### alibaba
```{r, echo=FALSE}
alibaba.p.t <- ts(alibaba$PRC, start = c(2015,1,1), frequency = 251.6)
summary(alibaba.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(alibaba.p.t, ylim=c(50,220),xlab="2015-2019",main="alibaba Closing Prices 01/01/2015-12/31/2019")

```


### Procter-Gamble
```{r, echo=FALSE}
pg.p.t <- ts(pg$PRC, start = c(2015,1,1), frequency = 251.6)
summary(pg.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(pg.p.t, ylim=c(60,130),xlab="2015-2019",main="pg Closing Prices 01/01/2015-12/31/2019")

```


### pfizer
```{r, echo=FALSE}
pfizer.p.t <- ts(pfizer$PRC, start = c(2015,1,1), frequency = 251.6)
summary(pfizer.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(pfizer.p.t, ylim=c(25,50),xlab="2015-2019",main="pfizer Closing Prices 01/01/2015-12/31/2019")

```


### johnson and johnson
```{r, echo=FALSE}
johnson.p.t <- ts(johnson$PRC, start = c(2015,1,1), frequency = 251.6)
summary(johnson.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(johnson.p.t, ylim=c(85,150),xlab="2015-2019",main="johnson&johnson Closing Prices 01/01/2015-12/31/2019")

```


### disney
```{r, echo=FALSE}
disney.p.t <- ts(disney$PRC, start = c(2015,1,1), frequency = 251.6)
summary(disney.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(disney.p.t, ylim=c(80,160),xlab="2015-2019",main="disney Closing Prices 01/01/2015-12/31/2019")

```


### wellsfargo
```{r, echo=FALSE}
wellsfargo.p.t <- ts(wellsfargo$PRC, start = c(2015,1,1), frequency = 251.6)
summary(wellsfargo.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(wellsfargo.p.t, ylim=c(40,70),xlab="2015-2019",main="wellsfargo Closing Prices 01/01/2015-12/31/2019")

```

### jpmorgan
```{r, echo=FALSE}
jpmorgan.p.t <- ts(jpmorgan$PRC, start = c(2015,1,1), frequency = 251.6)
summary(jpmorgan.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(jpmorgan.p.t, ylim=c(50,150),xlab="2015-2019",main="jpmorgan Closing Prices 01/01/2015-12/31/2019")

```

### walmart
```{r, echo=FALSE}
walmart.p.t <- ts(walmart$PRC, start = c(2015,1,1), frequency = 251.6)
summary(walmart.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(walmart.p.t, ylim=c(50,130),xlab="2015-2019",main="walmart Closing Prices 01/01/2015-12/31/2019")

```


### intel
```{r, echo=FALSE}
intel.p.t <- ts(intel$PRC, start = c(2015,1,1), frequency = 251.6)
summary(intel.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(intel.p.t, ylim=c(20,65),xlab="2015-2019",main="intel Closing Prices 01/01/2015-12/31/2019")

```

### Bank of America
```{r, echo=FALSE}
bankofa.p.t <- ts(bankofa$PRC, start = c(2015,1,1), frequency = 251.6)
summary(bankofa.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(bankofa.p.t, ylim=c(10,40),xlab="2015-2019",main="bankofa Closing Prices 01/01/2015-12/31/2019")

```


### verizon
```{r, echo=FALSE}
verizon.p.t <- ts(verizon$PRC, start = c(2015,1,1), frequency = 251.6)
summary(verizon.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(verizon.p.t, ylim=c(40,65),xlab="2015-2019",main="verizon Closing Prices 01/01/2015-12/31/2019")

```


### att
```{r, echo=FALSE}
att.p.t <- ts(att$PRC, start = c(2015,1,1), frequency = 251.6)
summary(att.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(att.p.t, ylim=c(25,45),xlab="2015-2019",main="att Closing Prices 01/01/2015-12/31/2019")

```

### Home Depot
```{r, echo=FALSE}
homedep.p.t <- ts(homedep$PRC, start = c(2015,1,1), frequency = 251.6)
summary(homedep.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(homedep.p.t, ylim=c(100,240),xlab="2015-2019",main="homedep Closing Prices 01/01/2015-12/31/2019")

```

### Citi Bank
```{r, echo=FALSE}
citi.p.t <- ts(citi$PRC, start = c(2015,1,1), frequency = 251.6)
summary(citi.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(citi.p.t, ylim=c(30,85),xlab="2015-2019",main="citi Closing Prices 01/01/2015-12/31/2019")

```


### amazon
```{r, echo=FALSE}
amazon.p.t <- ts(amazon$PRC, start = c(2015,1,1), frequency = 251.6)
summary(amazon.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(amazon.p.t, ylim=c(280,2040),xlab="2015-2019",main="amazon Closing Prices 01/01/2015-12/31/2019")

```


### China Mobile
```{r, echo=FALSE}
chinamob.p.t <- ts(chinamob$PRC, start = c(2015,1,1), frequency = 251.6)
summary(chinamob.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(chinamob.p.t, ylim=c(35,76),xlab="2015-2019",main="China Mobile Closing Prices 01/01/2015-12/31/2019")

```


### Taiwan SemiConductors
```{r, echo=FALSE}
taiwan.p.t <- ts(taiwan$PRC, start = c(2015,1,1), frequency = 251.6)
summary(taiwan.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(taiwan.p.t, ylim=c(18,60),xlab="2015-2019",main="Taiwan Semiconductors Closing Prices 01/01/2015-12/31/2019")

```


### Novartis
```{r, echo=FALSE}
novartis.p.t <- ts(novartis$PRC, start = c(2015,1,1), frequency = 251.6)
summary(novartis.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(novartis.p.t, ylim=c(65,110),xlab="2015-2019",main="novartis Closing Prices 01/01/2015-12/31/2019")

```

### visa
```{r, echo=FALSE}
visa.p.t <- ts(visa$PRC, start = c(2015,1,1), frequency = 251.6)
summary(visa.p.t)

```


### Visa split their stock in March 2015, hence the drop in price.
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(visa.p.t, ylim=c(63,280),xlab="2015-2019",main="visa Closing Prices 01/01/2015-12/31/2019")

```


### United Health
```{r, echo=FALSE}
unhealth.p.t <- ts(unhealth$PRC, start = c(2015,1,1), frequency = 251.6)
summary(unhealth.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(unhealth.p.t, ylim=c(90,300),xlab="2015-2019",main="United Health Closing Prices 01/01/2015-12/31/2019")

```


### Busch
```{r, echo=FALSE}
busch.p.t <- ts(busch$PRC, start = c(2015,1,1), frequency = 251.6)
summary(busch.p.t)

```
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(busch.p.t, ylim=c(60,135),xlab="2015-2019",main="Busch Closing Prices 01/01/2015-12/31/2019")

```


### netflix
```{r, echo=FALSE}
netflix.p.t <- ts(netflix$PRC, start = c(2015,1,1), frequency = 251.6)
summary(netflix.p.t)

```



#### Netflix split their stock in July 2015.
```{r, echo=FALSE}
par(mfrow=c(1,1), mex=0.75)
plot.ts(netflix.p.t, ylim=c(80,710),xlab="2015-2019",main="netflix Closing Prices 01/01/2015-12/31/2019")

```
